|

### 2023-01-19 inst/MyArticle/paper.Rmd
Added TOC to supplement. Further fixes related to renaming ContrastsSimpleImpute to ContrastsMissing

Where $n_g$ is the number of groups and $n$ is the number of observations.
If variance can not be estimated for a protein, because there are too few observations in other groups, we use the median pooled variance of all other proteins in the dataset. This method is implemented in the class `ContrastSimpleImpute` (see Figure \@ref(fig:ContrastUML)).

@@

```{r describeBenchmarkedModels, results='asis' }
xMM <- data.frame(
    msstats = c("MSstats", "preprocess with default parameters",  "", "evidence.txt"),
    msqrob = c("msqrob2::msqrobHurdle", "merge of msqrobHurdleIntensity and msqrobHurdleCount results", "protein and peptide", "peptide.txt"),
    proDA = c("proDA", "probabilistic dropout model",  "protein", "peptide.txt"),
    imputation = c("prolfqua_missing", "ContrastsMissing, ContrastsModerated", "protein",  "peptide.txt"),
    lmmed = c("prolfqua_lm_mod", "strategy_lm, Contrasts, ContrastsModerated",  "protein", "peptide.txt"),
    prot_merged = c("prolfqua_merged", "addContrastResults( prefer = proflqua_lm_mod , add = prolfqua_missing)HACKIT ",  "protein", "peptide.txt"),
    mixed = c("prolfqua_mix_eff_mod", "strategy_lmer, Contrasts, ContrastsModerated", "peptide", "peptide.txt" ),
    ROPECA = c("prolfqua_ropeca", "strategy_lm, Contrasts, ContrastsModerated, ContrastsROPECA", "peptide", "peptide.txt" )
)

xMM <- data.frame(t(xMM))
rownames(xMM) <- NULL
colnames(xMM) <-  c("Label","Description","Abundance","Input File")
tmp <- kableExtra::kable(xMM,
             caption = paste0("All benchmarked models. ",
             "Description - prolfqua function names, ",
             "Abudances - indicates if model is fitted to peptide or protein abundances, ",
             "Input File - name of MaxQuant file used as input."),
             format = "latex", booktabs = TRUE) |>
    kableExtra::kable_styling(latex_options = "scale_down") |> 
    kableExtra::add_footnote(label = "'prolfqua_merged' - Augments estimates which are missing in 'prot_med_lm_mod' with those from 'prot_impute'.")

@@

# Appendix  {.unnumbered}

>>>>

Where $n_g$ is the number of groups and $n$ is the number of observations.
If variance can not be estimated for a protein, because there are too few observations in other groups, we use the median pooled variance of all other proteins in the dataset. This method is implemented in the class `ContrastsMissing` (see Figure \@ref(fig:ContrastUML)).

@@

```{r describeBenchmarkedModels, results='asis' }
xMM <- data.frame(
    msstats = c("MSstats", "preprocess with default parameters",  "", "evidence.txt"),
    msqrob = c("msqrob2", "merge of msqrobHurdleIntensity and msqrobHurdleCount (msqrobHurdle)", "protein and peptide", "peptide.txt"),
    proDA = c("proDA", "probabilistic dropout model",  "protein", "peptide.txt"),
    imputation = c("prolfqua_missing", "ContrastsMissing, ContrastsModerated", "protein",  "peptide.txt"),
    lmmed = c("prolfqua_lm_mod", "strategy_lm, Contrasts, ContrastsModerated",  "protein", "peptide.txt"),
    prot_merged = c("prolfqua_merged", "addContrastResults( prefer = proflqua_lm_mod , add = prolfqua_missing)HACKIT ",  "protein", "peptide.txt"),
    mixed = c("prolfqua_mix_eff_mod", "strategy_lmer, Contrasts, ContrastsModerated", "peptide", "peptide.txt" ),
    ROPECA = c("prolfqua_ropeca", "strategy_lm, Contrasts, ContrastsModerated, ContrastsROPECA", "peptide", "peptide.txt" )
)

xMM <- data.frame(t(xMM))
rownames(xMM) <- NULL
colnames(xMM) <-  c("Label","Description","Abundance","Input File")
tmp <- kableExtra::kable(xMM,
             caption = paste0("All benchmarked models. ",
             "Label - name of the method, ", 
             "Description - functions used in the respective packages, ",
             "Abudances - indicates if model is fitted to peptide or protein abundances, ",
             "Input File - name of MaxQuant file used as input."),
             format = "latex", booktabs = TRUE) |>
    kableExtra::kable_styling(latex_options = "scale_down") |> 
    kableExtra::add_footnote(label = "'prolfqua_merged' - Augments estimates which are missing in 'prot_med_lm_mod' with those from 'prot_impute'.")

@@

### 2023-01-19 inst/MyArticle/prolfqua_supplement.Rmd
Added TOC to supplement. Further fixes related to renaming ContrastsSimpleImpute to ContrastsMissing

>>>>

(ref:toc) The figure illustrates some possible data analysis procedures that can
be achieved with only very few functions from prolfqua. As input
different levels from a variety of quantitation tools are accepted and
along with an annotation table configured for prolfqua using either
pre-built import functions or made ready with a little reshaping. In
prolfqua (depending on the input), one can choose roll-up
procedures and perform basic steps of mass spectrometry-based data
processing steps such as quality control, data normalization, protein
aggregation, as well as statistical modeling, hypothesis testing, and
sample size estimation. At all levels, one can always use
functions to show diagnostic plots or even inspect individual proteins.
Furthermore, prolfqua supports multiple models for differential
expression analysis such as linear (mixed effect) models and allows to
specify multiple contrasts.

```{r toc, echo=FALSE, fig.cap="(ref:toc)"}
knitr::include_graphics("graphics/TOCv2.pdf")
